---
title: "Data Journal Entry 7"
author: "Miranda Valencia"
date: "2025-04-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The following data is of the frequency of use of eleven basic color terms according to COCA (Corpus of Contemporary American English). The ten color terms are as followed: black, blue, brown, gray, green, orange, pink, purple, red, white, and yellow. This data is also categorized based on the genre / medium in which it appeared: spoken, fiction, academic, and press. However, for the sake of recreating figure A6 from Levshina's data, the "press" genre will be removed. The data will also be tidied to remove the rows in which the colors exist in to a separate column dedicated to color.


```{r}
### Setup with packages and working directory
library(tidyverse)
library(ggplot2)
load("~/Ling 490-2025 Data Analysis/week14/Rling_workspace.RData")
```

```{r}
### Loading Data
data(colreg)
colreg
```

```{r}
### Subsetting Data to remove "press" genre
colreg <- subset(colreg, select = c("spoken", "fiction", "academic"))
```

```{r}
### Separating the frequency data based on color for later
black <- unlist(colreg[1,], use.names = FALSE)
blue <- unlist(colreg[2,], use.names = FALSE)
brown <- unlist(colreg[3,], use.names = FALSE)
gray <- unlist(colreg[4,], use.names = FALSE)
green <- unlist(colreg[5,], use.names = FALSE)
orange <- unlist(colreg[6,], use.names = FALSE)
pink <- unlist(colreg[7,], use.names = FALSE)
purple <- unlist(colreg[8,], use.names = FALSE)
red <- unlist(colreg[9,], use.names = FALSE)
white <- unlist(colreg[10,], use.names = FALSE)
yellow <- unlist(colreg[11,], use.names = FALSE)
```

```{r}
###shifting the genres to a single column
colreg1 <- pivot_longer(colreg, cols = spoken:fiction:academic, names_to = "genre", values_to = "frequency")
```

```{r}
### Creating a new column for color association
colreg1$color = "seagreen"
```

```{r}
### Identifying the data with its coordinating color
colreg1$color[colreg1$frequency == black]= "black"
colreg1$color[colreg1$frequency == blue]= "blue"
colreg1$color[colreg1$frequency == brown]= "brown"
colreg1$color[colreg1$frequency == gray]= "gray"
colreg1$color[colreg1$frequency == green]= "green"
colreg1$color[colreg1$frequency == orange]= "orange"
colreg1$color[colreg1$frequency == pink]= "pink"
colreg1$color[colreg1$frequency == purple]= "purple"
colreg1$color[colreg1$frequency == red]= "red"
colreg1$color[colreg1$frequency == white]= "white"
colreg1$color[colreg1$frequency == yellow]= "yellow"
```

```{r}
### Column Names
colnames(colreg1)
### First few rows
head(colreg1)
```

```{r}
### Creating the A6 Figure
colreg1 %>%
  ggplot(aes(x= color, y= frequency, fill = genre))+
  geom_bar(stat = "identity", position = "dodge")+
  labs(title = "Basic Color Terms in COCA",
       x= "Color",
       y= "Frequency")+
  theme_minimal()
```

```{r}
write.csv(colreg1, file = "colreg")
```
